---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# MODISSnow

[![Travis-CI Build Status](https://travis-ci.org/jmsigner/MODISSnow.svg?branch=master)](https://travis-ci.org/jmsigner/MODISSnow)

`MODISSnow` allows to download MODIS snow data from [The National Snow & Ice Data Center](http://nsidc.org/).

# Quick start

## Install

Stable version von CRAN.

```{r, eval = FALSE}
install.packages("MODISSnow")
```

Or the dev version from GitHub.


```{r, eval = FALSE}
devtools::install_github("jmsigner/MODISSnow")
```

## Authentication

As of February 1st 2017, authentication via earthdata is requried. Free registration is possible at [the earthdata portal](https://urs.earthdata.nasa.gov/users/new).


## Workflow

```{r, eval = FALSE}
library(MODISSnow)
# Download MODIS snow data for a central Europe h = 18 and v = 5 for the 1 of January 2016
dat <- modissnow_get_data(lubridate::ymd("2016-01-01"), h = 18, v = 5, 
                          user = "username", passwd = "password", sat = "MYD10A1")
class(dat)
raster::plot(dat)
```

# Meta
- Please report [any issues or bugs](https://github.com/ropensci/gistr/issues).
- License: GPL v3
- Get citation information for `MODISSnow` in R typing `citation(package = 'MODISSnow')`.
- Please note that this project is released with a [Contributor Code of Conduct](CONDUCT.md). By participating in this project you agree to abide by its terms.
